Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-24 doc/main_jfm.tex
updates

The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the mean friction force and the mean slip velocity. This quantity is given by 
\begin{equation}
b = \frac{\langle F_f\rangle}{\langle\int_{\Sigma_M} R \dot\theta \dif s\rangle},
\end{equation}
%
where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the midplane and the centroid of the Janus-vesicle. Hence, the mean rotational velocity 
of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
For the friction force $F_f$, we integrate tangential stresses near the bilayer from outer and inner regions then 
extrapolate the force value onto the midplane $\Sigma_M$ to acquire the force difference. 
Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
within the same order, the friction coefficients are independent of the shear rates.

>>>>

The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the mean friction force and the mean slip velocity. This quantity is given by 
\begin{equation}
b = \frac{\langle F_f\rangle}{\langle\int_{\Sigma_M} R \dot\theta \dif s\rangle},
\end{equation}
%
where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the midplane and the centroid of the Janus-vesicle. Hence, the mean rotational velocity 
of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
For the friction force $F_f$, we integrate tangential stresses near the bilayer from outer and inner regions then 
extrapolate the force value onto the midplane $\Sigma_M$ to acquire the force difference. 
Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$ which are quantitatively close to literature~\cite{sch-vla-mik2010,denOtter2007}.

%As expected, within the same order, the friction coefficients are independent of the shear rates.
